### 2023-11-28 main.tex
Section 4.2

\section{Correlations and steady state  for the integrable chain}\label{sectionIntegrabiliy}
In this section we combine duality and the matrix product ansatz (MPA) to charaterize the non-equilibrium steady state for the integrable version of the multispecies stirring process, defined in Section~\ref{integrableChain-duality}. 
As it will turn out, such combination of duality and MPA allows to determine a closed formula for the absorption probabilities and thus (using Corollary~\ref{Corolollary-ABS_Corr-abstract}) for the correlations
and (using Corollary~\ref{Corollary-NESS-ABS}) for the probability mass-function of the non-equilibrium steady state.
We start by recalling the formulation of the MPA  and then we explain our strategy.

@@

\subsection{Strategy}
 In the next Section~\ref{subsection-exact} we will show that the existence of the absorbing dual process established in Section~\ref{sectionDuality} simplifies substantially the algebra of operators $X_a$ defined in previous
 section.  The idea is summarized in the following scheme. 

@@

 where $H^{'}= S_{1} H S_{1}^{-1} $ has both boundary terms in a triangular form, and $H^{''} = S_{2}H' S_{2}^{-1}$ has the left boundary in a triangular form and the right boundary is diagonal. Using these transformations the commutators \eqref{bulk} and the action on the boundary vectors \eqref{leftBoundary}, \eqref{rightBoundary} become simpler. As a consequence, the ground state $|\Psi^{''}\rangle$ of $H^{''}$ can be written explicitly. Finally, reversing the transformations we retrieve $|\Psi\rangle$, i.e. the vector whose components are the probabilities of a certain configuration of the process in the non-equilibrium steady state.

@@

@@

	\langle W|\left((\alpha_{a}-\beta_{a})\Xt_{N}-\Xt_{a}\right)=(\alpha_{a}-\beta_{a})\langle\co W|%\qquad\forall a=1,\ldots,N-1

@@

>>>>

\section{Correlations and steady state  for the integrable chain}\label{sectionIntegrabiliy}
In this section we combine duality, the $gl(N)$ invariance and the matrix product ansatz (MPA) to charaterize the non-equilibrium steady state for the integrable version of the multispecies stirring process, defined in Section~\ref{integrableChain-duality}. 
As it will turn out, the combination of the $gl(N)$ invariance  and the MPA allows to determine a closed formula for the absorption probabilities and thus (using Corollary~\ref{Corolollary-ABS_Corr-abstract}) for the correlations
and (using Corollary~\ref{Corollary-NESS-ABS}) for the probability mass-function of the non-equilibrium steady state.
We start by recalling the formulation of the MPA  and then we explain our strategy.

@@

\subsection{Strategy}
 In the next Section~\ref{subsection-exact} we will show that the DEHP albegra in \eqref{bulk}-\eqref{rightBoundary} can be simplified substantially using the ${gl}(N)$ invariance of the bulk. In fact, such simplification can always be achieved if 
  there exists an absorbing dual process as established in Section~\ref{sectionDuality}

 The idea is summarized in the following scheme. 

@@

 where $H^{'}= S_{1} H S_{1}^{-1} $ has both boundary terms in a triangular form, and $H^{''} = S_{2}H' S_{2}^{-1}$ has the left boundary in a triangular form and the right boundary is diagonal. Using these transformations the commutators \eqref{bulk} and the action on the boundary vectors \eqref{leftBoundary}, \eqref{rightBoundary} simplify significantly. More precisely for the components of $\tilde X=S_2S_1 X$ we obtain the bulk relations
\begin{equation}\label{commutationsBula2}
for $a=1,\ldots,N-1$. 
At the boundaries 
\begin{equation}\label{commLEFT2}
	\langle W|\left((\alpha_{a}-\beta_{a})\Xt_{N}-\Xt_{a}\right)=(\alpha_{a}-\beta_{a})\langle W|%\qquad\forall a=1,\ldots,N-1
	\co \qquad 
	\,.
where again we have  $a=1,\ldots,N-1$.   As a consequence, the ground state $|\Psi^{''}\rangle$ of $H^{''}$ can be written exactly in closed-form. Finally, reversing the transformations we retrieve $|\Psi\rangle$, i.e. the vector whose components are the probabilities of a certain configuration of the process in the non-equilibrium steady state.

@@

	\left[\Xt_{a},\Xt_{N}\right]=(\alpha_{a}-\beta_{a})\Xt_{N}\co %\forall a\in \{1,\ldots,N-1\}\dt
cf.~\eqref{commutationsBula2}.

@@

	\langle W|\left((\alpha_{a}-\beta_{a})\Xt_{N}-\Xt_{a}\right)=(\alpha_{a}-\beta_{a})\langle W|%\qquad\forall a=1,\ldots,N-1
	\co

@@

	\co
cf.~\eqref{commLEFT2}.
